\begin{center}
	\renewcommand{\arraystretch}{1.3}
	\begin{longtabu}{c X}
		\caption{List of identified risks and solutions, sorted according to type} \label{tab:security-list} \\
		\hline
			\multicolumn{1}{c}{\textbf{Ref.*}}	&	\textbf{Description} \\
		\hline
			\multicolumn{2}{c}{Procedural problems \& risks} \\
		\hline
			\cite{s4Layman2008}, \ref{security-first-interview}	&	Data aggregation and cross referencing makes the identification of individuals possible. \\
			\cite{s18Kum2014}	&	Applying secondary data analysis makes it difficult to cover purpose in the consent process. \\
			\cite{s18Kum2014}	&	Data linkage without identifying data is impossible, data linkage with identifying data is unsafe. \\
			\cite{s18Kum2014}	&	In data linkage privacy has to be temporarily breached in order to identify matching entities in two datasets. \\
			\cite{s18Kum2014}	&	Finding the right amount of identifying data for linkage is a difficult task. \\
			\ref{security-first-interview}	&	Determining identifying data is open to interpretation. \\
		\\ %whitespace
			\multicolumn{2}{c}{Procedural solutions} \\
		\hline
			\cite{s3Herveg2014}	&	Personal data can only be used for the purposes described when the consent was given by the subject. \\
			\cite{s3Herveg2014, s6West2009, s18Kum2014}, \ref{security-first-interview}	&	Data being used should be in a minimum dataset, no superfluous data should be present. \\
			\cite{s3Herveg2014, s15Fenz2014}	&	After the purpose described in the consent has been reached identifying data should be removed from the dataset. \\
			\cite{s3Herveg2014}	&	The purpose of data usage should be: ``specified, explicit, and legitimate''. \\
			\cite{s8FernandezAleman2013}	&	At any point in time and audit of data should be kept, \ie{} provenance of data. \\
			\cite{s8FernandezAleman2013}	&	Accountability is a central part of security. \\
			\cite{s15Fenz2014, s13Patil2014}	&	Apply anonymisation and pseudonymisation to protect identifiable data or to make it impossible to use this data to identify individuals while still being able to use this data for analytical purposes. \\
			\ref{security-first-interview}	&	For each debatable data item describe the purpose it fulfils. \\
		\\ %whitespace
			\multicolumn{2}{c}{Technical solutions} \\
		\hline
			\cite{s6West2009}	&	Use hashes of identifying data to refer to individuals, which is usable for analytical purposes but not for identifying individuals in the real world. \\
			\cite{s6West2009}	&	Store a specified data structure on a secure server. \\
			\cite{s11Rauscher2014}	&	Use ``portholes'' to view data, \ie{} aggregate data for the user to view but do no disclose the dataset. \\
			\cite{s11Rauscher2014}	&	Declassify data when output is requested by the user, hereby removing identifiable data. \\
			\cite{s16Ma2013}	&	Separate identifying data from dataset, in this paper applied to optimise search. Non-identifying data is available for fast search, after making a selection identifying data is appended before outputting. \\
			\cite{s18Kum2014}	&	Using hashes together with (for example) Bloom filters provide a solution to using identifiable data in data linkage. \\
			\ref{security-first-interview}	&	Take note of standard security measures of the present and implement those. \\
	\end{longtabu}
	\par \bigskip
	*: Reference, either refers to a citation (with brackets []) or an interview (paragraph numbering \eg{} 1.2.1)
\end{center}
%PROCEDURAL
%solution
%TODO: 6 Limited dataset under 45 CFR §164.514(e): 'Under certain circumstances, a covered entity may use and disclose protected health information (PHI) in a limited dataset for research, public health, and health care operations purposes. The privacy regulation identifies a list of identifiers that must be removed from data in order for it to be considered a “limited dataset”. Once removed, the information is not deidentified – it is still PHI governed by the privacy regulation. A data use agreement must be signed by those wishing to use limited datasets.'