\paragraph{NVOG}
Nederlandse Vereniging voor Obstetrie en Gynaecologie (Dutch association of obstetrics and gynaecology), institution looking after the interests of the Dutch obstetrics and gynaecology domain.

\paragraph{IUI}
Intrauterine Insemination, an assisted reproduction technique.

\paragraph{ICSI}
intracytoplasmic sperm injection, an assisted reproduction technique.

\paragraph{\IVF{}} 
In Vitro Fertilisation, an assisted reproduction technique.
In this paper also used to denote the medical domain of fertilisation.

\paragraph{\PRN{}}
Perinatale Registratie Nederland (Dutch national perinatal registration), registration containing all perinatal data from the Netherlands.
The registry exists of population based data on pregnancies, provided care, deliveries and (re)admissions of newborns.

\paragraph{\project{}} 
Dutch Assisted Reproductive Technology Study, a encompassing body covering multiple studies concerning assisted reproductive technologies.
In this paper used to denote the study concentrating on linking data from fertility clinics with \PRN{} data.

\paragraph{\projectdata{}}
\project{} dataset, dataset containing the linked data from fertility clinics and the \PRN{}.

\paragraph{\ivfsystem{}}
\project{} gateway, project name for the development of the system described in this paper.

\paragraph{SPSS, SAS, and R}
Popular statistical software packages.

\paragraph{EHR}
Electronic Health Record, software package collecting health information on patients.
Replaces the paper health record.

\paragraph{AMC}
Academic Medical Centre, university hospital in Amsterdam.
Institution where this study was conducted at.

\paragraph{NSG}
NeuroScience Gateway, web application providing an user friendly interface for managing data, processings, and community.
Stores image references and metadata on MRI data.
Provides support for processing this data with specific applications.

\paragraph{MRI}
Magnetic Resonance Imaging, technique used for scanning (parts of) the human body.

\paragraph{\ivfprototype{}}
\project{} prototype, name for the implemented prototype of the \ivfsystem{}.

\paragraph{CTM}
Clinical Trial Management, refers to a type of software used to gather and store data when conducting a clinical trial.

\paragraph{XNAT}
Data storage service specifically designed for storing MRI images and metadata.