4 pages

\begin{itemize}
	\item What are the biggest blocking factors in doing research with sensitive data and how can these be overcome?
	\item What is the importance of supporting administrative tasks (provides security, better understanding, etc.)? 
	\item How can this specific system be used in other settings/knowledge domains?
\end{itemize}

\section{Overview and Implications}
Give short overview of all the chapters (outcomes/results).
What are the outcome of the requirement analysis, design, software implementation, cases, and evaluation steps?

%\begin{itemize}
%	\item How was security integrated into the functionality and data model.
%	\item How was security and provenance accounted for, how does provenance help with security (auditing, which is also a function)?
%	\item How was this reflected in the software engineering
%	\item How was the system structured to help researchers, data managers, and PI's?
%	\item Was this reflected in the outcomes of the cases and/or evaluation?
%	\item What are the strengths and weaknesses of this study and this system particularly?
%	\item What other systems were discussed and what were their strengths and weaknesses?
%	\item How is this system going to help clinicians, researchers, managers, policy makers (government?)?
%	\item What questions remain unanswered and what needs to be done on the system to complete it? 
%	\item Can it be extrapolated to other backgrounds?
%\end{itemize}

\section{Appraisal}
\paragraph{Strengths and limitations}
One registry as example (no branching to other domains). 
Limited time to program, thus less implemented functionality.
However, this example provides many different angles to approach the problem.
\paragraph{Comparison with existing systems}
Comparison with other existing software (OpenClinica, etc)
\paragraph{Future research and development considerations}
What functions need to be implemented to give the system an extra `boost'.
How can the system manage the expectations of users better.
How can the system better support users in their data management tasks.

\section{Conclusion}
Answer the questions stated in the introduction.