10 pages

\section{Introduction}
\paragraph{Problem}
Describe data `usage' phases and what the problems are now:
\begin{itemize}
	\item Study preparation, data usage approval
	\item Data retrieval
	\item Data massaging/preparation
	\item Data analysis
	\item Data reuse
\end{itemize}
\paragraph{Position}
There should be more data re-use and cooperation between data producers/consumers.
IT can help with the alignment of these two factions.

\section{Background and Evidence}
How is research performed now?
Describe Dutch law on privacy and data usage.
Explain how METC and commissions influence data usage.
Talk about clinicians.
Patient willingness to share their data for research.
Big data and its general stance on data usage.

\section{Discussion}
(Limitations):
\begin{itemize}
	\item How does Dutch law prescribe security and ethics to be taken into consideration and why does this matter, what is the fear?
	\item Is law taken into account in the right manner every time?
	\item How do METC, commissions, and other influential bodies limit the use of data?
	\item What are the clinician's opinion, thoughts, and `holding back' in fear of rebuttal
	\item What are expected hold-ups for research now (data gathering can take extremely long)?
	\item Will patients withhold their data for use in research and why?
\end{itemize}
(Chances):
\begin{itemize}
	\item What does existing big data research describe is necessary in order to conduct successful and meaningful studies?
	\item What are some necessities for a certain fluidity in using sensitive data for research?
	\item How to can limitations be aligned with the big data opportunities
	\item What needs to be changed in attitude in order to open up data reuse and sharing (introduce Scandinavian ideas)?
	\item How can online and offline (IT) be leveraged to bring convincing and easy-to-grasp ideas to inspire people to change their way of working?
\end{itemize}
Give both sides of the issue and discuss how these two can be aligned with each other to meet at a sweet spot for both factions.

\section{Conclusion}
\paragraph{Further steps}
Figure out if IT can be leveraged to align medical and technical personnel.
\paragraph{Proposing solutions}
IT leverage in the form of a system (like the one in this thesis).